Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution

### 2018-05-28 manuscript.tex

With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respecitvely) , and present advantages and limitations for both of these choices in Sec. \ref{sec:4} and Sec. \ref{sec:5}. 
The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.

>>>>

With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respectively) , and present advantages and limitations for both of these choices in Sec. \ref{sec:4} and Sec. \ref{sec:5}. 
The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.
